Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-04-23 TC-4.18.tex
update

 An interesting feature found in our simulations is that there are a pair of innermost bubbles\
 (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma\
 and probably not related to the X-ray chimneys \citep{Ponti2019}\
 and radio bubbles \citep{Heywood2019}\
 due to their enormous difference in length (the total major-axis length of the X-ray chimneys
 and radio bubbles is 320 pc and 430 pc, respectively; however, the innermost bubbles
 is up to 4 kpc in length).
 The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
 and slices (Fig. \ref{fig__innerbubbles})\
 demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\ %{\color{red} KY: Is it verified that the reverse shock is expanding outward? PH: Yes. I have checked that with multiple slices in different time. The reverse shock is expanding outward.}
 The high-density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, there exists a dense shell before the gas density drops to values further downstream.
 %Continuing outward, the higher density must match with low density further downstream;\
 %thus there exists a dense shell.\
 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

>>>>

 An interesting feature found in our simulations is that there are a pair of innermost bubbles\
 (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma\
 but probably not related to the X-ray chimneys \citep{Ponti2019}\
 and radio bubbles \citep{Heywood2019}\
 due to their enormous difference in length (the total major-axis length of the X-ray chimneys
 and radio bubbles is 320 pc and 430 pc, respectively; however, the innermost bubbles
 is up to 4 kpc in length).
 The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
 and slices (Fig. \ref{fig__innerbubbles})\
 demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\ %{\color{red} KY: Is it verified that the reverse shock is expanding outward? PH: Yes. I have checked that with multiple slices in different time. The reverse shock is expanding outward.}
 The high-density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, there exists a dense shell before the gas density drops to values further downstream.
 %Continuing outward, the higher density must match with low density further downstream;\
 %thus there exists a dense shell.\
 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.
